What We Eval in the Shadows

### 2021-04-14 analysis/usage.Rmd
Fix figures in Usage metrics

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma) +
  labs(x = "nodes") +
  theme(text = element_text(size=17),  panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), aspect.ratio = 4/3)

@@

# Plot the low trigger counts...
triggered %>%
  filter(average < 50) %>%
  ggplot(aes(x = average)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.3, colour = "black") +
  theme(text = element_text(size=16), 
        axis.text = element_text(size=20), 
        aspect.ratio = 4/3)

>>>>

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma) +
  labs(x = "Nodes", y = "Count") +
  theme(text = element_text(size=17),  panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), aspect.ratio = 4/3)

@@

# Plot the low trigger counts...
triggered %>%
  filter(average < 50) %>%
  ggplot(aes(x = average)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.3, colour = "black") +
  labs(x = "Average", y = "Count") +
  theme(text = element_text(size=16), 
        axis.text = element_text(size=20), 
        aspect.ratio = 4/3)

### 2021-04-14 paper/main.tex
Fix figures in Usage metrics

  \vspace*{-1mm}
  \includegraphics[width=5.6cm, trim=5.5cm 0 5cm 0, clip]{calls_per_run_per_call_site}

@@

\begin{tabular}{c}
  \vspace*{-1mm}
  {\hspace{-3cm}\includegraphics[width=0.8\textwidth]{size_loaded_distribution}}
\end{tabular}
 \caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

@@

\begin{figure}[tb!]
\begin{tabular}{@{}c@{}c@{}}
\begin{minipage}{7.5cm}
 \includegraphics[width=\textwidth]{events_per_pack_small}
\end{minipage}&\begin{minipage}{7.5cm}
  \includegraphics[width=\textwidth]{events_per_pack_large}
\end{minipage}\\[-3mm]
\small (a) Small & \small (b) Large
\end{tabular}
 \caption{Instructions per call} \label{ev}
\end{figure}

>>>>

  \vspace*{-1mm}
  \includegraphics[width=5.6cm, trim=5.5cm 0 5cm 0, clip]{package_calls_per_run_per_call_site}

@@

\begin{tabular}{c}
  \vspace*{-1mm}
  {\hspace{-3cm}\includegraphics[width=0.8\textwidth]{package_size_loaded_distribution}}
\end{tabular}
 \caption{Loaded code} \label{fig:sizedistribution}
\end{wrapfigure}

@@

\begin{figure}[tb!]
\begin{tabular}{@{}c@{}c@{}}
\begin{minipage}{7.5cm}
 \includegraphics[width=\textwidth]{package_events_per_pack_small}
\end{minipage}&\begin{minipage}{7.5cm}
  \includegraphics[width=\textwidth]{package_events_per_pack_large}
\end{minipage}\\[-3mm]
\small (a) Small & \small (b) Large
\end{tabular}
 \caption{Instructions per call} \label{ev}
\end{figure}
